Visualising CHD Pathway Inequalities by ethnicity - DRAFT

### 2024-03-14 draft_report.qmd
Corrected error in text

The relative index of deprivation for the metric is expressed here as a %, such that the % indicates the amount of activity that would need to be redistributed between clusters in order that event rates follow levels of need. The detail of the methodology used for its calculation can be found in the appendix.

>>>>

The relative index of disparity for the metric is expressed here as a %, such that the % indicates the amount of activity that would need to be redistributed between clusters in order that event rates follow levels of need. The detail of the methodology used for its calculation can be found in the appendix.

### 2024-03-14 findings.qmd
Corrected error in text

|---------------|---------------|---------------|---------------|---------------|

@@

| Risk factors               | Smoking synthetic prevalence estimates | GP survey   | 2023    |                                                                                         |
| Risk factor identification | Smoking register                       | NHSD QOF    | 2022/23 | [Indicator 91280 extracted fromFingertipsR](https://fingertips.phe.org.uk/search/91280) |
|                            | Obesity register                       | NHSD QOF    |         | [Indicator 93088 extracted fromFingertipsR](https://fingertips.phe.org.uk/search/93088) |
|                            | Diabetes register                      | NHSD QOF    |         |                                                                                         |
|                            | Depression register                    | NHSD QOF    |         |                                                                                         |
| Primary prevention         |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
|                            |                                        |             |         |                                                                                         |
| Full Outcomes              | Deaths in hospital from CHD            |             |         |                                                                                         |
|                            | Deaths in hospital from CHD \< 75      |             |         |                                                                                         |
|                            | Deaths from CHD                        |             |         |                                                                                         |
|                            | Deaths from CHD \<75                   |             |         |                                                                                         |

>>>>

|-------------|-----------------|-------------|-------------|----------------|

@@

| Risk factors               | Smoking synthetic prevalence estimates                                                                                                                                                                                                                 | GP Survey   | 2023    |                                                                                          |
| Risk factor identification | Smoking register                                                                                                                                                                                                                                       | NHSD QOF    | 2022/23 | [Indicator 91280 extracted from FingertipsR](https://fingertips.phe.org.uk/search/91280) |
|                            | Obesity register                                                                                                                                                                                                                                       | NHSD QOF    | 2022/23 | [Indicator 93088 extracted from FingertipsR](https://fingertips.phe.org.uk/search/93088) |
|                            | Diabetes register                                                                                                                                                                                                                                      | NHSD QOF    | 2022/23 | [Indicator 241 extracted from FingertipsR](https://fingertips.phe.org.uk/search/241)     |
|                            | Depression register                                                                                                                                                                                                                                    | NHSD QOF    | 2022/23 | [Indicator 848 extracted from FingertipsR](https://fingertips.phe.org.uk/search/848)     |
|                            | The percentage of patients aged 45 or over who have a record of blood pressure in the preceding 5 years                                                                                                                                                | NHSD QOF    | 2022/23 | [Indicator 91262 extracted from FingertipsR](https://fingertips.phe.org.uk/search/91262) |
|                            | CVD risk register                                                                                                                                                                                                                                      | NHSD QOF    | 2019/20 | Formerly indicator 92589 extracted from FingertipsR                                      |
| Primary prevention         | Percentage of patients aged 18 and over with GP recorded CVD (narrow definition), who are currently treated with lipid lowering therapy                                                                                                                | CVD Prevent | 2022/23 | <https://www.cvdprevent.nhs.uk/home>                                                     |
|                            | Percentage of patients aged 18 and over, with no GP recorded CVD and a GP recorded QRISK score of 10% or more, CKD (G3a to G5), T1 diabetes (aged 40 and over) or T2 diabetes aged 60 and over, who are currently treated with lipid lowering therapy. | CVD Prevent | 2022/23 | <https://www.cvdprevent.nhs.uk/home>                                                     |
|                            | Smoking cessation support offered                                                                                                                                                                                                                      | NHSD QOF    | 2022/23 | [Indicator 90619 extracted from FingertipsR](https://fingertips.phe.org.uk/search/90619) |
|                            | Exception reporting for Smoking cessation support offered                                                                                                                                                                                              | NHSD QOF    | 2022/23 | [Indicator 90619 extracted from FingertipsR](https://fingertips.phe.org.uk/search/90619) |
| Disease Identification     | CHD register                                                                                                                                                                                                                                           | NHSD QOF    | 2022/23 | [Indicator 273 extracted from FingertipsR](https://fingertips.phe.org.uk/search/273)     |
|                            | CT angiography                                                                                                                                                                                                                                         | SUS         | 2022/23 | OPCS Code: U102 - Cardiac                                                                |

```         
                                                                                                                                                                                                                                                                                                                    computed tomography angiography.                                                                        
                                                                                                                                                                                                                                                                                                                    Elective only                                                                                           |
```

|                            \| Electrocardiography \| SUS \| 2022/23 \| OPCS: U19 & U34. Elective only \|
| Secondary Prevention \| Aspirin, anti-platelet or anti-coagulent \| NHSD QOF \| 2022/23 \| [Indicator 90999 extracted from FingertipsR](https://fingertips.phe.org.uk/search/90999) \|
|                            \| Exception reporting for Aspirin, anti-platelet or anti-coagulent \| NHSD QOF \| 2022/23 \| [Indicator 90999 extracted from FingertipsR](https://fingertips.phe.org.uk/search/90999) \|
|                            \| Percentage of patients aged 65 or over who received a seasonal influenza vaccination between 1 September 2022 and 31 March 2023 \| IIF \| March 2023 \| <https://www.england.nhs.uk/primary-care/primary-care-networks/network-contract-des/iif/> \|
|                            \| Percentage of patients aged 18 to 64 years and in a clinical at-risk group who received a seasonal influenza vaccination between 1 September 2022 and 31 March 2023 \| IIF \| March 2023 \| <https://www.england.nhs.uk/primary-care/primary-care-networks/network-contract-des/iif/> \|
|                            \| Referral to cardiology (First outpatient) \| SUS \| 2022/23 \| TFC = 320 \|
|                            \| Cardiology outpatient DNAs \| SUS \| 2022/23 \| TFC = 320 \|
| Tertiary Prevention \| Elective PCI \| SUS \| 2022/23 \| OPCS Code: K49, K50, K75. FCE = 1 \|
|                            \| Elective CABG \| SUS \| 2022/23 \| OPCS Code: K40-K46, FCE = 1 \|
|                            \| Waiting time for elective PCI / CABG \| SUS \| 2022/23 \| Elective admissions. OPCS Codes as per metrics 20 and 21 \|
|                            \| Elective PCI / CABG patients discharged before trimpoint \| SUS \| 2022/23 \| Main PCI and CABG Trim points for 2022/23 linked for HRG \|
|                            \| Cardiac rehabilitation - Started \| NACR \| 2023 \| Data supplied by ICB. Aggregated ACS and HF patients. \|
|                            \| Cardiac rehabilitation - Completed \| NACR \| 2023 \| Data supplied by ICB. Aggregated ACS and HF patients. \|
| Intermediate Outcomes \| Last BP reading of patients (\<80 yrs, with CHD) in last 12mths is \<=140/90 \| NHSD QOF \| 2022/23 \| CHD008 \|
|                            \| Readmission within 30 days of elective PCI / CABG \| SUS \| 2022/23 (MarFeb) \| No. of emerg. spells up to 31/03/2023 within 0-29 days (inclusive) of the last, previous discharge from hospital / No. of finished spells with discharge date between 01/03/2022 and 28/02/2023 Exclude: TFC = 501, 560, 610, OPCS starting with O, Classpat = 1 (Ord.), Any diagnosis = C00\*-C97\*, D37\*-D48\* \|
|                            \| Emergency admissions for CHD \| SUS \| 2022/23 \| PRIMARY diagnosis = I20 or I21 or I22 or I23 or I24 or I25 \|
| Full Outcomes \| Deaths in hospital from CHD \| SUS \| 2022/23 \| Following any admission Elective or Emergency. PRIMARY diagnosis = I20 or I21 or I22 or I23 or I24 or I25 \|
|                            \| Deaths in hospital from CHD \< 75 \| SUS \| 2022/23 \| Following any admission Elective or Emergency. PRIMARY diagnosis = I20 or I21 or I22 or I23 or I24 or I25. Age \<=75 \|
|                            \| Deaths from CHD \| ONS Death records \| 2022/23 \| Underlying Cause of Death = I20 or I21 or I22 or I23 or I24 or I25 \|
|                            \| Deaths from CHD \<75 \| ONS Death records \| 2022/23 \| Underlying Cause of Death = I20 or I21 or I22 or I23 or I24 or I25. Age \<=75 \|
